quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-02 paper-quollr.Rmd
Updated merge_hexbin_cetroid description

This function begins by arranging the `counts_data` by `h` to ensure consistent ordering. It then performs a full join with `centroids_data`, aligning hexagon IDs (`h`) between the two datasets to incorporate both hexagonal bin centroids (`h`) and count metrics. After merging, the function handles missing values in the count columns: any `NA` values in `w_h` or `n_h` are replaced with zeros. This ensures that hexagons with no assigned data points are retained in the output, with zero values for count-related fields. The resulting data contains the full set of hexagon centroids along with associated bin counts (`n_h`) and standardized counts (`w_h`).

>>>>

This function performs a full join with `centroids_data`, aligning hexagon IDs (`h`) between the two datasets to incorporate both hexagonal bin centroids (`h`) and count metrics. After merging, the function handles missing values in the count columns: any `NA` values in `w_h` or `n_h` are replaced with zeros. This ensures that hexagons with no assigned data points are retained in the output, with zero values for count-related fields. The resulting data contains the full set of hexagon centroids along with associated bin counts (`n_h`) and standardized counts (`w_h`).

### 2025-12-02 paper-quollr.tex
Updated merge_hexbin_cetroid description

This function begins by arranging the \texttt{counts\_data} by \texttt{h} to ensure consistent ordering. It then performs a full join with \texttt{centroids\_data}, aligning hexagon IDs (\texttt{h}) between the two datasets to incorporate both hexagonal bin centroids (\texttt{h}) and count metrics. After merging, the function handles missing values in the count columns: any \texttt{NA} values in \texttt{w\_h} or \texttt{n\_h} are replaced with zeros. This ensures that hexagons with no assigned data points are retained in the output, with zero values for count-related fields. The resulting data contains the full set of hexagon centroids along with associated bin counts (\texttt{n\_h}) and standardized counts (\texttt{w\_h}).

>>>>

This function performs a full join with \texttt{centroids\_data}, aligning hexagon IDs (\texttt{h}) between the two datasets to incorporate both hexagonal bin centroids (\texttt{h}) and count metrics. After merging, the function handles missing values in the count columns: any \texttt{NA} values in \texttt{w\_h} or \texttt{n\_h} are replaced with zeros. This ensures that hexagons with no assigned data points are retained in the output, with zero values for count-related fields. The resulting data contains the full set of hexagon centroids along with associated bin counts (\texttt{n\_h}) and standardized counts (\texttt{w\_h}).
